An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
adds another secref
Signed-off-by: andrew <andrew@textile.io>

Like many CQRS-based systems, the “public” API for Threads revolves around the concept of Views (see background section xxx), which are used to optimize queries on the local event store. A key feature of Views is they are completely disposable, because they can be entirely rebuilt from the source event store. In Threads, Views are updated by subscribing to specific Event(s), and applying a Reducer function that is used to update the View state (which may be materialized to local persistent storage). This simple subscription system provides a flexible framework for building complex View-driven application logic.

@@

In practice, Snapshots are written to their own Event log and stored locally. They can potentially be synced (see section 3.2.4) to other peers as a form of data backup or to optimize state initialization when a new peer starts participating in a shared Thread (saving disk space, bandwidth, and time). They can similarly be used for initializing state during recovery.

>>>>

Like many CQRS-based systems, the “public” API for Threads revolves around the concept of Views, which are used to optimize queries on the local event store. A key feature of Views is they are completely disposable, because they can be entirely rebuilt from the source event store. In Threads, Views are updated by subscribing to specific Event(s), and applying a Reducer function that is used to update the View state (which may be materialized to local persistent storage). This simple subscription system provides a flexible framework for building complex View-driven application logic.

@@

In practice, Snapshots are written to their own Event log and stored locally. They can potentially be synced (see Section \ref{sec:LogSync}) to other peers as a form of data backup or to optimize state initialization when a new peer starts participating in a shared Thread (saving disk space, bandwidth, and time). They can similarly be used for initializing state during recovery.
